Results Text

### 2023-04-19 Fish Data Analysis/Paper_Figures.qmd
Updated figures

dark_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Darkness == "Dark"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory\nConditions")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2),
        legend.position = "none")

ablation_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory\nConditions")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2),
        legend.position = "none")

light_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory\nConditions")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2),
        legend.position = "none")

@@

### Turning Stats Table Here

```{r}
turning_glm_still <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
                         data = annushka_turning_data %>% filter(Flow == "Still Water"), family = binomial)
tgs_aov <- Anova(turning_glm_still)

turning_glm_flow <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
                         data = annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family = binomial)
tgf_aov <- Anova(turning_glm_flow)

turning_results <- tibble(Flow_or_Still = c("Still","Still","Still","Still","Still","Flow","Flow","Flow","Flow","Flow"),
       Factor = c("Fish_Num_Ratio","Ablation","Darkness","Fish_Num_Ratio:Ablation","Fish_Num_Ratio:Darkness",
                  "Fish_Num_Ratio","Ablation","Darkness","Fish_Num_Ratio:Ablation","Fish_Num_Ratio:Darkness"),
       DF = c(rep(length(turning_glm_still$y)-3,5),rep(length(turning_glm_flow$y)-3,5)),
       LR_Chisq = c(tgs_aov$`LR Chisq`,tgf_aov$`LR Chisq`),
       P_Val = c(tgs_aov$`Pr(>Chisq)`,tgf_aov$`Pr(>Chisq)`),
       Is_Sig = P_Val < 0.05)

# Single vs Eight fish
light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
                               family = binomial)
ltg_aov <- Anova(light_turning_glm)

ablated_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
                               family = binomial)
altg_aov <- Anova(ablated_turning_glm)

dark_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Darkness == "Dark"),
                               family = binomial)
dtg_aov <- Anova(dark_turning_glm)

single_vs_eight_results <- tibble(Condition = c("Light","Light","Ablated","Ablated","Darkness","Darkness"),
       Factor = c("Type","FNR:Type","Type","FNR:Type","Type","FNR:Type"),
       DF = c(rep(length(light_turning_glm$y)-3,2),rep(length(ablated_turning_glm$y)-3,2),rep(length(dark_turning_glm$y)-3,2)),
       LR_Chisq = c(ltg_aov$`LR Chisq`[2:3],altg_aov$`LR Chisq`[2:3],dtg_aov$`LR Chisq`[2:3]),
       P_Val = c(ltg_aov$`Pr(>Chisq)`[2:3],altg_aov$`Pr(>Chisq)`[2:3],dtg_aov$`Pr(>Chisq)`[2:3]),
       Is_Sig = P_Val < 0.05)

turning_results
single_vs_eight_results

@@

turning_single_test_plot <- ggarrange(
          light_eight_and_single_graph, ablation_eight_and_single_graph, dark_eight_and_single_graph,
          labels = c("A", "B", "C"),
          ncol = 3, nrow = 1)

ggsave("Paper Figures/turning_single_test_plot.png", turning_single_test_plot, width = 9, height = 3)

@@

speed_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,6)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time") +
    theme_light()+ 
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#e63946")) +
    theme(axis.text.x = element_text(size = text_size),
          axis.text.y = element_text(size = text_size),
          axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

group_flow <- ggplot(group_sum_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time") +
    theme_light()+ 
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#e63946")) +
    theme(axis.text.x = element_text(size = text_size),
          axis.text.y = element_text(size = text_size),
          axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

### School Stats Table Here

nnd_glmer_still <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
nnd_s_aov_me <- Anova(nnd_glmer_still)

nnd_glmer_flow <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
nnd_f_aov_me <- Anova(nnd_glmer_flow)

height_glmer_still <- lmer(School_Height ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
height_s_aov_me <- Anova(height_glmer_still)

height_glmer_flow <- lmer(School_Height ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
height_f_aov_me <- Anova(height_glmer_flow)

polar_glmer_still <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
polar_s_aov_me <- Anova(polar_glmer_still)

polar_glmer_flow <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
polar_f_aov_me <- Anova(polar_glmer_flow)

speed_glmer_still <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
speed_s_aov_me <- Anova(speed_glmer_still)

speed_glmer_flow <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
speed_f_aov_me <- Anova(speed_glmer_flow)

area_glmer_still <- lmer(Area ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
area_s_aov_me <- Anova(area_glmer_still)

area_glmer_flow <- lmer(Area ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
area_f_aov_me <- Anova(area_glmer_flow)

groups_glmer_still <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
groups_s_aov_me <- Anova(groups_glmer_still)

groups_glmer_flow <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
groups_f_aov_me <- Anova(groups_glmer_flow)

glmm_school_stats_table <- tibble(Stat = c(rep("NND",4),rep("Height",4),rep("Polarization",4),rep("Speed",4),rep("Area",4),rep("Groups",4)),
       Flow_or_Still = rep( c(rep("Still",2) , rep("Flow",2)), 6),
       Condition = rep(c("Ablation","Darkness"), 12),
       DF = rep(c(length(nnd_glmer_still@resp$y)-3,length(nnd_glmer_flow@resp$y)-3),12),
       Chisq = c(nnd_s_aov_me$Chisq[1:2],nnd_f_aov_me$Chisq[1:2],
                 height_s_aov_me$Chisq[1:2],height_f_aov_me$Chisq[1:2],
                 polar_s_aov_me$Chisq[1:2],polar_f_aov_me$Chisq[1:2],
                 speed_s_aov_me$Chisq[1:2],speed_f_aov_me$Chisq[1:2],
                 area_s_aov_me$Chisq[1:2],area_f_aov_me$Chisq[1:2],
                 groups_s_aov_me$Chisq[1:2],groups_f_aov_me$Chisq[1:2]),

       P_Val = c(nnd_s_aov_me$`Pr(>Chisq)`[1:2],nnd_f_aov_me$`Pr(>Chisq)`[1:2],
                 height_s_aov_me$`Pr(>Chisq)`[1:2],height_f_aov_me$`Pr(>Chisq)`[1:2],
                 polar_s_aov_me$`Pr(>Chisq)`[1:2],polar_f_aov_me$`Pr(>Chisq)`[1:2],
                 speed_s_aov_me$`Pr(>Chisq)`[1:2],speed_f_aov_me$`Pr(>Chisq)`[1:2],
                 area_s_aov_me$`Pr(>Chisq)`[1:2],area_f_aov_me$`Pr(>Chisq)`[1:2],
                 groups_s_aov_me$`Pr(>Chisq)`[1:2],groups_f_aov_me$`Pr(>Chisq)`[1:2]),

       Is_Sig = P_Val < 0.05)

glmm_school_stats_table

nnd_glm_still <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
nnd_s_aov <- Anova(nnd_glm_still)

nnd_glm_flow <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
nnd_f_aov <- Anova(nnd_glm_flow)

height_glm_still <- glm(School_Height ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
height_s_aov <- Anova(height_glm_still)

height_glm_flow <- glm(School_Height ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
height_f_aov <- Anova(height_glm_flow)

polar_glm_still <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
polar_s_aov <- Anova(polar_glm_still)

polar_glm_flow <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
polar_f_aov <- Anova(polar_glm_flow)

speed_glm_still <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
speed_s_aov <- Anova(speed_glm_still)

speed_glm_flow <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
speed_f_aov <- Anova(speed_glm_flow)

area_glm_still <- glm(Area ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
area_s_aov <- Anova(area_glm_still)

area_glm_flow <- glm(Area ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
area_f_aov <- Anova(area_glm_flow)

groups_glm_still <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
groups_s_aov <- Anova(groups_glm_still)

groups_glm_flow <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
groups_f_aov <- Anova(groups_glm_flow)

glm_school_stats_table <- tibble(Stat = c(rep("NND",4),rep("Height",4),rep("Polarization",4),rep("Speed",4),rep("Area",4),rep("Groups",4)),
       Flow_or_Still = rep( c(rep("Still",2) , rep("Flow",2)), 6),
       Condition = rep(c("Ablation","Darkness"), 12),
       DF = rep(c(length(nnd_glm_still$y)-3,length(nnd_glm_flow$y)-3),12),
       Chisq = c(nnd_s_aov$`LR Chisq`[1:2],nnd_f_aov$`LR Chisq`[1:2],
                 height_s_aov$`LR Chisq`[1:2],height_f_aov$`LR Chisq`[1:2],
                 polar_s_aov$`LR Chisq`[1:2],polar_f_aov$`LR Chisq`[1:2],
                 speed_s_aov$`LR Chisq`[1:2],speed_f_aov$`LR Chisq`[1:2],
                 area_s_aov$`LR Chisq`[1:2],area_f_aov$`LR Chisq`[1:2],
                 groups_s_aov$`LR Chisq`[1:2],groups_f_aov$`LR Chisq`[1:2]),

       P_Val = c(nnd_s_aov$`Pr(>Chisq)`[1:2],nnd_f_aov$`Pr(>Chisq)`[1:2],
                 height_s_aov$`Pr(>Chisq)`[1:2],height_f_aov$`Pr(>Chisq)`[1:2],
                 polar_s_aov$`Pr(>Chisq)`[1:2],polar_f_aov$`Pr(>Chisq)`[1:2],
                 speed_s_aov$`Pr(>Chisq)`[1:2],speed_f_aov$`Pr(>Chisq)`[1:2],
                 area_s_aov$`Pr(>Chisq)`[1:2],area_f_aov$`Pr(>Chisq)`[1:2],
                 groups_s_aov$`Pr(>Chisq)`[1:2],groups_f_aov$`Pr(>Chisq)`[1:2]),

       Is_Sig = P_Val < 0.05)

glm_school_stats_table

sum(glm_school_stats_table$Is_Sig == glmm_school_stats_table$Is_Sig)
sum(glm_school_stats_table$Is_Sig == 1 & glmm_school_stats_table$Is_Sig == 1) / sum(glm_school_stats_table$Is_Sig == 1)

@@

>>>>

placeholder_tibble <- tibble("Fish_Ratio" = c("0:7","0:7","3:4"),
                             "Fish_Num_Ratio" = c(0.875,0.875,0.5),
                             "Flow" = c("Still Water","Still Water","Still Water"),
                             "Ablation" = c("No Ablation","Ablated","Ablated"),
                             "Darkness" = c("Light","Light","Light"),
                             "Type" = c("Combined Single","Combined Single","Combined Single"),
                             "n" = c(0,0,0))

turning_data_sum <- turning_data_sum %>% ungroup()

turning_data_sum <- full_join(turning_data_sum,placeholder_tibble)

dark_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Darkness == "Dark"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

ablation_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

light_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type, color = none), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

@@

@@

turning_single_test_plot <- ggarrange(
          light_eight_and_single_graph, ablation_eight_and_single_graph, dark_eight_and_single_graph,
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2)

ggsave("Paper Figures/turning_single_test_plot.png", turning_single_test_plot, width = 10, height = 7)

@@

speed_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=max(Speed_Mean_Val-Speed_SD_Val,0), ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,6)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time") +
    theme_light()+ 
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#3ae639")) +
    theme(axis.text.x = element_text(size = text_size),
          axis.text.y = element_text(size = text_size),
          axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

group_flow <- ggplot(group_sum_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time") +
    theme_light()+ 
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#3ae639")) +
    theme(axis.text.x = element_text(size = text_size),
          axis.text.y = element_text(size = text_size),
          axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

@@

Autocorrelation Figure

school_data_no_removals <- read.csv("Data/Fish_School_Values_3D.csv")
school_data_no_removals <- na.omit(school_data_no_removals)

school_data_no_removals <- school_data_no_removals %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed <= 5) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Date = paste(Year,Month,Day,sep="_"),
                                  Date_Trial = paste(Year,Month,Day,Trial,sep="_"),)

for(i in seq(1:5)){
  print(i)

  new_autocorrs <- school_data_no_removals %>% group_by(Date_Trial) %>%
                    filter(!Date_Trial %in% c("2021_3_25_30","2020_7_28_29")) %>%
                    summarise(nnd_corr = abs(cor.test(NND, lag(NND, n = i))$estimate),
                              nnd_p = cor.test(NND, lag(NND, n = i))$p.value,
                              polar_corr = abs(cor.test(School_Polar, lag(School_Polar, n = i))$estimate),
                              polar_p = cor.test(School_Polar, lag(School_Polar, n = i))$p.value,
                              speed_corr = abs(cor.test(School_Speed, lag(School_Speed, n = i))$estimate),
                              speed_p = cor.test(School_Speed, lag(School_Speed, n = i))$p.value,
                              groups_corr = abs(cor.test(Groups, lag(Groups, n = i))$estimate),
                              groups_p = cor.test(Groups, lag(Groups, n = i))$p.value,
                              area_corr = abs(cor.test(Area, lag(Area, n = i))$estimate),
                              area_p = cor.test(Area, lag(Area, n = i))$p.value,
                              height_corr = abs(cor.test(School_Height, lag(School_Height, n = i))$estimate),
                              height_p = cor.test(School_Height, lag(School_Height, n = i))$p.value,
                              lag = i)

  if(i == 1){
    school_autocorrs <- new_autocorrs
  }
  else{
    school_autocorrs <- rbind(school_autocorrs,new_autocorrs) 
  }

}

nnd_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), nnd_corr))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("NND Autocorrelation")+
  xlab("Offest")+
  theme_classic()+ 
  theme(legend.position = "none")

polar_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), polar_corr))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("Polarity Autocorrelation")+
  xlab("Offest")+
  theme_classic()+ 
  theme(legend.position = "none")

speed_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), speed_corr))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("Speed Autocorrelation")+
  xlab("Offest")+
  theme_classic()+ 
  theme(legend.position = "none")

groups_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), groups_corr))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("Numebr of Groups Autocorrelation")+
  xlab("Offest")+
  theme_classic()+ 
  theme(legend.position = "none")

lag_plots <- ggarrange(
          nnd_lag_plot, polar_lag_plot, speed_lag_plot, groups_lag_plot,
          ncol = 2, nrow = 2,
          labels = c("A", "B", "C", "D"))

ggsave("Paper Figures/Different_Lag_Figures.png", lag_plots, width = 7, height = 7)

### 2023-04-19 Fish Data Analysis/Results_Text.qmd
Updated figures

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
```

@@

@@

turning_results
single_vs_eight_results
```

>>>>

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
library(sjPlot)
```

@@

tab_df(glmm_school_stats_table, file="sjt_des.doc")
```

@@

turning_results
single_vs_eight_results

tab_df(single_vs_eight_results, file="sjt_des.doc")
```
